Plant trait cleaning and combining

### 2024-09-03 code/L1/L1_P4_TropicalAndes_plant_traits.Rmd
change plot colors and other plot customizations

# Create the faceted bar plot with free y-axis scales
ggplot(trait_counts, aes(x = DatabaseSource, y = n, fill = DatabaseSource)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Trait Counts per Database",
       x = "Trait Name",
       y = "Trait Count",
       fill = "Database Source") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ TraitName, scales = "free_y")
ggsave("plant_trait_counts_per_database.png", plot = last_plot(), path = figure_path)
```

>>>>

# Customize fill color of database
custom_colors <- c("BIEN" = "#a6cf3c" , "GIFT" = "#009900", "TRY" = "#40a353")

# Create the faceted bar plot
ggplot(trait_counts, aes(x = DatabaseSource, y = n, fill = DatabaseSource)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Trait Counts per Database",
       x = "Trait Name",
       y = "Trait Count",
       fill = "Database Source") +
  scale_fill_manual(values = custom_colors) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") +
  facet_wrap(~ TraitName, scales = "free_y", nrow = 2)
ggsave("plant_trait_counts_per_database.png", plot = last_plot(), path = figure_path, width = 12, height = 5)
```
